\documentclass[a4paper,12pt]{article}
\usepackage{usual}

\usepackage[a4paper, margin=1in]{geometry}

\setlength{\parindent}{0pt}
\setstretch{1.2}

\newcommand{\ti}[1]{\textit{#1}}

% ===============================================================================================================

\title{Pondering about Astro-Cosmo Stuff!}
\author{tamuli}
\date{}

\begin{document}

\maketitle

\begin{abstract}
  Some of the lines and questions from the books invoke ideas in my mind connecting various different topics and subjects I've learnt, especially quantum information. So here's a jumbled plethora of all of those where I just ramble about bullshit! yayyyyyyyyyy!
\end{abstract}

\tableofcontents

\newpage

\section{Entanglement and Viewing the Past!}
\ti{To understand the
formation and evolution of the Galaxy, a view of its (and
thus our own) past would be useful. Unfortunately, this is
physically impossible.}

\vspace{1em}

quotes \ti{Schneider}\cite{ref:Schneider-astro} and I wonder, what if... we observe an entangled particle from far away? Say we have two entangled particles, one with us and one very far away, will we be able to discover the past of our own particle since we will be receiving communication from far away and hence the past?

\vspace{1em}

Can this be extended to bigger systems and is there a chance systems in our universe have been entangled? Can that even happen? Kind of needs to be a question of its own.

\section{Can Entanglement happen Naturally?}

Can it just happen without any external interference (no pun intended)? Hmmmmm im curious.

\end{document}
